---
title: "R Notebook"
output: html_notebook
---

US Temperature - Time Series Analysis with predictions for next 18 days. 

```{r}
temp = read.csv("https://raw.githubusercontent.com/katariyj/Time-Series-in-R-Project/master/abc.csv")
```

```{r}
temp
```

```{r}
head(temp)
tail(temp)
```

```{r}
summary(temp)
```

```{r}
dim(temp)
```

```{r}
hist(x = temp$Starts)
```

```{r}
str(temp)
```
```{r}
names(temp)
```

```{r}
plot(temp$Starts, type = "l", col="red")
```

```{r}
# Advance EDA
library(ggplot2)
```

```{r}
qplot(temp$Starts, fill = I("blue"), 
      alpha = I(.5), col= I("red"),
      xlab = "Temperature",  
      main="Histogram of US Temperature Index", 
      bins = 25)
```

```{r}


ggplot(temp, aes(x = temp$Starts))+ 
  geom_density(color="red", fill="blue", alpha= 0.4)+ 
  xlab("Temperature")+ 
  ggtitle("Frequency Density Plot of Temperature")


```

```{r}

library(ggfortify)
library(stats)
library(forecast)
temp_start = ts(temp$Starts)
temp_start1 = ts(temp$Starts, frequency = 15)


autoplot(stl(temp_start1, s.window = 'periodic'), 
         ts.colour = 'blue')

ggtsdisplay(temp_start, 
            main = "Temp Trend, ACF, PACF Plot")

```


Transformations and EDA - Log of Temperature
```{r}
logtemp = log(temp_start)

logtemp1 = ts(logtemp, frequency = 15)


autoplot(stl(logtemp1, s.window = 'periodic'), ts.colour = 'blue')

ggtsdisplay(logtemp1, main = "Log Temperature Trend, ACF, PACF Plot")
```
Transformations and EDA -Differencing of Temperature
```{r}
diff_temp = diff(temp_start1)


autoplot(stl(diff_temp, s.window = 'periodic'))

ggtsdisplay(diff_temp, main = "Differencing of Temperature Trend, ACF, PACF Plot")
```
Transformations and EDA -Double Differencing of Temperature
```{r}
double_diff_temp = diff(diff_temp)


autoplot(stl(double_diff_temp, s.window = 'periodic'))

ggtsdisplay(double_diff_temp, main = "Double Differencing of Temperature Trend, ACF, PACF Plot")
```

Transformations and EDA -Differencing of Log Temperature
```{r}
diff_logtemp = diff(logtemp1)


autoplot(stl(diff_logtemp, s.window = 'periodic'), ts.colour = 'blue')

ggtsdisplay(diff_logtemp, main = "Differencing of Log Temperature Trend, ACF, PACF Plot")
```
Transformations and EDA -Double Differencing of Log Temperature
```{r}
double_diff_logtemp = diff(diff(logtemp1))


autoplot(stl(double_diff_logtemp, s.window = 'periodic'), ts.colour = 'blue')

ggtsdisplay(double_diff_logtemp, main = "Differencing of Log Temperature Trend, ACF, PACF Plot")
```
# This is good

```{r}
seasonal_diff_nolog = (diff(temp_start1, 12))
autoplot(stl(seasonal_diff_nolog, s.window = 'periodic'), ts.colour = 'blue')

ggtsdisplay(seasonal_diff_nolog, main = "Differencing of NO Log Temperature Trend, ACF, PACF Plot")
```


```{r}
seasonal_diff_temp_log = (diff(logtemp1, 12))
autoplot(stl(seasonal_diff_temp_log, s.window = 'periodic'), ts.colour = 'blue')

ggtsdisplay(seasonal_diff_temp_log, main = "Differencing of Log Temperature Trend, ACF, PACF Plot")

```
# This is Bad.
```{r}
seasonal_diff = diff((diff(logtemp1, 12)),12)
autoplot(stl(seasonal_diff, s.window = 'periodic'), ts.colour = 'blue')

ggtsdisplay(seasonal_diff, main = "Differencing of Log Temperature Trend, ACF, PACF Plot")
```

Compare Histogram of  temperature and diff_log_temperature 
```{r}

require(gridExtra)
seasonal_diff_Temp_nolog = qplot(seasonal_diff_nolog, fill = I("green"), alpha = I(.5), col= I("red"),xlab = "Seasonal Differencing of Temperature",  main="Seasonal Differencing of Temperature", bins = 25)

Seasonal_diff_logtemp=qplot(seasonal_diff_temp_log, fill = I("blue"), alpha = I(.5), col= I("red"),xlab = "Seasonal Differencing of Log Temperature",  main="Seasonal Differencing of Log Temperature", bins = 25)
grid.arrange(seasonal_diff_Temp_nolog, Seasonal_diff_logtemp, ncol=2)

```
Model on Original Data

```{r}
m1=arima(temp_start,order=c(4,0,0),seasonal=list(order=c(0,1,2),period=12))

m1
Box.test(m1$resid,lag=10,type='Ljung') 
autoplot(acf(m1$resid, plot = FALSE))

tsdiag(m1)
```

```{r}
m2=arima(temp_start,order=c(4,0,4),seasonal=list(order=c(0,1,1),period=12))

m2
Box.test(m2$resid,lag=10,type='Ljung') 
autoplot(acf(m2$resid, plot = FALSE))

tsdiag(m1)
```

Model on Log data 

```{r}
m3=arima(logtemp,order=c(4,0,0),seasonal=list(order=c(0,1,2),period=12))

m3
Box.test(m3$resid,lag=10,type='Ljung') 
autoplot(acf(m3$resid, plot = FALSE))

tsdiag(m3)

library(fUnitRoots)
adfTest(m3$residuals)
```

```{r}
m4=arima(logtemp,order=c(4,0,6),seasonal=list(order=c(0,1,1),period=12))

m4
Box.test(m4$resid,lag=10,type='Ljung') 
autoplot(acf(m4$resid, plot = FALSE))

tsdiag(m4)

adfTest(m4$residuals)
```

```{r}
m5=arima(logtemp,order=c(4,0,0),seasonal=list(order=c(0,1,1),period=12))

m5
Box.test(m5$resid,lag=10,type='Ljung') 
autoplot(acf(m5$resid, plot = FALSE))

tsdiag(m5)

adfTest(m5$residuals)

```

```{r}
m6=arima(logtemp,order=c(4,0,6),seasonal=list(order=c(0,1,2),period=12))

m6
Box.test(m6$resid,lag=10,type='Ljung') 
autoplot(acf(m6$resid, plot = FALSE))

tsdiag(m6)

adfTest(m6$residuals)
```


```{r}

m7=arima(logtemp,order=c(4,0,4),seasonal=list(order=c(0,1,1),period=12))

m7
Box.test(m7$resid,lag=10,type='Ljung') 
autoplot(acf(m7$resid, plot = FALSE))

tsdiag(m7)

adfTest(m7$residuals)
```

```{r}

```

Forecasting for next n months

```{r}
source("fore.R")
source("foreplot.R")
source("backtest.R")


pl = fore(m7, logtemp, 181, 8)
foreplot(pl, logtemp, 181,0)


```

```{r}
library(forecast)

plot(forecast(m7, h= 10))

lines(logtemp, col = "green")
```

Cross-Validation
```{r}
library(caTools)

split = sample.split(logtemp, SplitRatio = 0.90)
train= subset(logtemp, split==TRUE)
print(train)
test = subset(logtemp, split==FALSE)


m_train=arima(train,order=c(4,0,4),seasonal=list(order=c(0,1,1),period=12))
m_train

```


```{r}
pred= predict(m_train, 18)

error = test - pred$pred
error
```

```{r}
accuracy(pred$pred, test)
```

```{r}
poly1=c(1,-m_train$coef[1:3])
roots=polyroot(poly1)
roots

Mod(roots)
```
